### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@82b7a567b4d655f1b771a049e0c23faba83917bd 🚀

\textbf{P1}

@@

\textbf{P2}

@@

\textbf{P3}

@@

\textbf{P4}

@@

\textbf{P6}

But forecasting is only half the story---if indeed ``{[}ecologists{]}
have hitherto only interpreted the world in various ways; the point is
to change it,'' then once we have a forecast about how an ecosystem will
change in the future, what if this forecast predicts a critical
ecosystem service will deteriorate? We are still left with the question,
what do we in the time being to mitigate the negative consequences a
forecast predicts? In this framing, mitigating the consequences of
anthropogenic change on ecosystems becomes an optimization problem:
given a forecast of the probability. We have some goal state for the
future, and some estimate of what the state of the world will be given a
set of actions. Frame optimization problem mathematically an introduce
concept of solution-space and constraint.

@@

\textbf{P7}

This dissertation aims to formalize a framework for ecosystem monitoring
and forecasting (fig.~\ref{fig:thesis}, left), and each chapter address
some aspect of this pipeline to data from a monitoring network to
forecasts to mitigation strategy (fig.~\ref{fig:thesis}, right).

@@

Interactions between plants and pollinators form networks of
interactions, which structure the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The functioning and stability of ecosystems
emerge from these interactions, but antropogenic change threatens to
unravel and ``rewire'' these networks (\textbf{CaraDonna2017IntRew?}),
threating the persistence of these systems. Plant-pollinator networks
face two possible forms of rewiring in response to anthropogenic
environmental change: spatial and temporal.\\
Spatially, range shifts could cause interacting species to no longer
overlap in space, and shifts in phenology could cause interacting
species to no longer overlap in time.

@@

This also goes on to includes testing some assumptions of the model with
empirical data fig.~\ref{fig:posassoc}, which we analytically show that
our neutral model, if anything, underestimates the probability of
false-negatives due to positive correlations in co-occurrence in two
spatially replicated networks (Thompson \& Townsend 2000; Hadfield
\emph{et al.} 2014)---further I'm planning to add the field data from
the previous chapter into this anlysis once available.

@@

\begin{itemize}
\tightlist
\item
  brief overview of simulated annealing
\item
  describe how you build the proposal function
\item
  optimize landscape optimization
\end{itemize}

>>>>

@@

@@

@@

@@

But forecasting is only half the story---if indeed ``{[}ecologists{]}
have hitherto only interpreted the world in various ways; the point is
to change it,'' then once we have a forecast about how an ecosystem will
change in the future, what if this forecast predicts a critical
ecosystem service will deteriorate? We are still left with the question,
what do we in the time being to mitigate the potentially negative
consequences a forecast predicts? In this framing, mitigating the
consequences of anthropogenic change on ecosystems becomes an
optimization problem: given a forecast of the future state of the
system, and some ``goal'' state for the future, the problem is then to
optimize our intervention into the system to maximize the probability
the system approaches our ``goal'' state. This dissertation aims to this
framework for ecosystem monitoring and forecasting
(fig.~\ref{fig:thesis}, left), and each chapter address some aspect of
this pipeline to data from a monitoring network to forecasts to
mitigation strategy (fig.~\ref{fig:thesis}, right).

@@

@@

Interactions between plants and pollinators form networks of
interactions, which structure the ``architecture of biodiversity''
(\textbf{Jordano2007?}). The functioning and stability of ecosystems
emerge from these interactions, but antropogenic change threatens to
unravel and ``rewire'' these networks (\textbf{CaraDonna2017IntRew?}),
threating the persistence of these systems. Plant-pollinator networks
face two possible forms of rewiring in response to anthropogenic
environmental change: spatial and temporal. Spatially, range shifts
could cause interacting species to no longer overlap in space, and
shifts in phenology could cause interacting species to no longer overlap
in time.

@@

This also goes on to includes testing some assumptions of the model with
empirical data fig.~\ref{fig:posassoc}, which we analytically show that
our neutral model, if anything, underestimates the probability of
false-negatives due to positive correlations in co-occurrence in two
sets of spatially replicated samples of interaction networks (Thompson
\& Townsend 2000; Hadfield \emph{et al.} 2014)---further I'm planning to
add the field data from the previous chapter into this anlysis once
available.

@@

\begin{itemize}
\tightlist
\item
  brief overview of simulated annealing describe how you build the
\item
  proposal function optimize landscape optimization
\end{itemize}
